Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Updated curosities

algo_obj_gau1 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_gau, 
  nldr_data = tsne_data_gau, 
  num_x_bins = num_bins_x_gau1)

tsne_gau_scaled <- algo_obj_gau1$nldr_scaled
tr_from_to_df_gau1 <- algo_obj_gau1$tr_from_to_df
df_bin_centroids_gau1 <- algo_obj_gau1$df_bin_centroids
df_bin_gau1 <- algo_obj_gau1$df_bin

@@

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 75
algo_obj_gau1 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_gau, 
  nldr_data = umap_data_gau, 
  num_x_bins = num_bins_x_gau1)

umap_gau_scaled <- algo_obj_gau1$nldr_scaled
tr_from_to_df_gau1 <- algo_obj_gau1$tr_from_to_df
df_bin_centroids_gau1 <- algo_obj_gau1$df_bin_centroids
df_bin_gau1 <- algo_obj_gau1$df_bin

@@

algo_obj_gau1 <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_gau, 
  nldr_data = pacmap_data_gau, 
  num_x_bins = num_bins_x_gau1)

pacmap_gau_scaled <- algo_obj_gau1$nldr_scaled
tr_from_to_df_gau1 <- algo_obj_gau1$tr_from_to_df
df_bin_centroids_gau1 <- algo_obj_gau1$df_bin_centroids
df_bin_gau1 <- algo_obj_gau1$df_bin

@@

algo_obj_dens_clust <- gen_nldr_vis_algo_obj(
  high_d_data = one_c_shaped_data, 
  nldr_data = tsne_one_c_shaped, 
  num_x_bins = num_bins_x_one_c_shaped)

tsne_one_c_shaped_scaled <- algo_obj_dens_clust$nldr_scaled
tr_from_to_df_dens_clust <- algo_obj_dens_clust$tr_from_to_df
df_bin_centroids_dens_clust <- algo_obj_dens_clust$df_bin_centroids
df_bin_dens_clust <- algo_obj_dens_clust$df_bin
hex_grid_with_counts_dens_clust <- algo_obj_dens_clust$hex_grid_with_counts
```

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  num_x_bins = num_bins_x_pbmc)

umap_pbmc_scaled <- algo_obj_pbmc$nldr_scaled
tr_from_to_df_pbmc <- algo_obj_pbmc$tr_from_to_df
df_bin_centroids_pbmc <- algo_obj_pbmc$df_bin_centroids
df_bin_pbmc <- algo_obj_pbmc$df_bin

@@

df_bin_centroids_pbmc <- df_bin_centroids_pbmc |>
  dplyr::filter(std_counts > 0)

@@

algo_obj_pbmc <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_pbmc, 
  nldr_data = tsne_pbmc, 
  num_x_bins = num_bins_x_tsne_pbmc)

tsne_pbmc_scaled_best <- algo_obj_pbmc$nldr_scaled
distance_pbmc <- algo_obj_pbmc$distance_df
tr_from_to_df_pbmc <- algo_obj_pbmc$tr_from_to_df
df_bin_centroids_pbmc <- algo_obj_pbmc$df_bin_centroids
df_bin_pbmc <- algo_obj_pbmc$df_bin

@@

df_bin_centroids_pbmc <- df_bin_centroids_pbmc |>
  dplyr::filter(std_counts > 0)

>>>>

algo_obj_gau1 <- fit_highd_model(
  highd_data = training_data_gau, 
  nldr_data = tsne_data_gau, 
  bin1 = num_bins_x_gau1, 
  q = 0.1, 
  benchmark_highdens = 5)

tsne_gau_scaled <- algo_obj_gau1$nldr_obj$scaled_nldr
tr_from_to_df_gau1 <- algo_obj_gau1$trimesh_data
df_bin_centroids_gau1 <- algo_obj_gau1$model_2d
df_bin_gau1 <- algo_obj_gau1$model_highd

@@

# df_bin_centroids_gau1 <- df_bin_centroids_gau1 |>
#   dplyr::filter(std_counts > 0)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 75

algo_obj_gau1 <- fit_highd_model(
  highd_data = training_data_gau, 
  nldr_data = tsne_data_gau, 
  bin1 = num_bins_x_gau1, 
  q = 0.1, 
  benchmark_highdens = 5)

tsne_gau_scaled <- algo_obj_gau1$nldr_obj$scaled_nldr
tr_from_to_df_gau1 <- algo_obj_gau1$trimesh_data
df_bin_centroids_gau1 <- algo_obj_gau1$model_2d
df_bin_gau1 <- algo_obj_gau1$model_highd

@@

algo_obj_gau1 <- fit_highd_model(
  highd_data = training_data_gau, 
  nldr_data = tsne_data_gau, 
  bin1 = num_bins_x_gau1, 
  q = 0.1, 
  benchmark_highdens = 5)

tsne_gau_scaled <- algo_obj_gau1$nldr_obj$scaled_nldr
tr_from_to_df_gau1 <- algo_obj_gau1$trimesh_data
df_bin_centroids_gau1 <- algo_obj_gau1$model_2d
df_bin_gau1 <- algo_obj_gau1$model_highd

@@

algo_obj_dens_clust <- fit_highd_model(
  highd_data = one_c_shaped_data, 
  nldr_data = tsne_one_c_shaped, 
  bin1 = num_bins_x_one_c_shaped, 
  q = 0.1, 
  benchmark_highdens = 5)

tsne_one_c_shaped_scaled <- algo_obj_dens_clust$nldr_obj$scaled_nldr
tr_from_to_df_dens_clust <- algo_obj_dens_clust$trimesh_data
df_bin_centroids_dens_clust <- algo_obj_dens_clust$model_2d
df_bin_dens_clust <- algo_obj_dens_clust$model_highd
```

@@

algo_obj_pbmc <- fit_highd_model(
  highd_data = training_data_pbmc, 
  nldr_data = umap_pbmc, 
  bin1 = num_bins_x_pbmc, 
  q = 0.1, 
  benchmark_highdens = 5)

umap_pbmc_scaled <- algo_obj_pbmc$nldr_obj$scaled_nldr
tr_from_to_df_pbmc <- algo_obj_pbmc$trimesh_data
df_bin_centroids_pbmc <- algo_obj_pbmc$model_2d
df_bin_pbmc <- algo_obj_pbmc$model_highd

@@

# df_bin_centroids_pbmc <- df_bin_centroids_pbmc |>
#   dplyr::filter(std_counts > 0)

@@

algo_obj_pbmc <- fit_highd_model(
  highd_data = training_data_pbmc, 
  nldr_data = tsne_pbmc, 
  bin1 = num_bins_x_tsne_pbmc, 
  q = 0.1, 
  benchmark_highdens = 5)

tsne_pbmc_scaled_best <- algo_obj_pbmc$nldr_obj$scaled_nldr
tr_from_to_df_pbmc <- algo_obj_pbmc$trimesh_data
df_bin_centroids_pbmc <- algo_obj_pbmc$model_2d
df_bin_pbmc <- algo_obj_pbmc$model_highd

@@
